---
title: "Rocket League"
author: "David Young"
date: "2022-07-22"
output: pdf_document
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE)
# dataset https://www.kaggle.com/datasets/dylanmonfret/rlcs-202122?resource=download&select=matches_by_teams.csv
setwd("C:/DataViz/RL")
library(ggplot2)
library(dplyr)
library(readr)
library(sqldf)
library(psych)

# gt = read_csv("games_by_teams.csv") #Games at the Team level
# gp = read_csv("games_by_players.csv") #Games at the player level

mp = read_csv("https://github.com/Derek-Kirk/Rocket_League/blob/cd8b6dbbf3577b8280e1d32b914d24f25a799784/matches_by_players.csv?raw=true") #Matches at the player level
#mp$scored_core_goal = ifelse(mp$core_goals > 0, 1, 0)

mt = read_csv("https://github.com/Derek-Kirk/Rocket_League/blob/cd8b6dbbf3577b8280e1d32b914d24f25a799784/matches_by_teams.csv?raw=true") #Matches at the team level

```

#Working with Competetive player data from matches **Questions that I want to answer:** 1.

```{r column names, include = FALSE}
colnames(mp)
```

```{r, creating dataset}
joined_data = read_csv("https://github.com/Derek-Kirk/Rocket_League/blob/main/joined_data.csv?raw=true")[,2:12]
# joined_data = sqldf("select mt.team_name,
# mt.color, 
# mp.player_tag,
# mp.core_goals,
# mp.core_assists, 
# mp.core_saves, 
# mp.core_shots,
# mp.core_score,
# mp.demo_inflicted,
# mp.demo_taken,
# mp.advanced_rating
# from mt
#       left join mp on mp.team_id = mt.team_id
#       and mp.match_id = mt.match_id
#       where mp.demo_taken is not null")
# joined_data$team_name = as.factor(joined_data$team_name)
# joined_data$color = as.factor(joined_data$color)
# joined_data$player_tag = as.factor(joined_data$player_tag)
```



# Checking for missing data

Below is a list of variables where players are missing data from the limited data set. After going through and looking at handful of the variables, I have determined that if one of the variables is null, all variables for the case are null for this for these "non-standard statistics"

```{r, include=FALSE}
vars_with_NA = c()
for(x in colnames(joined_data)){
  #print(x)
  tble = sqldf(paste("select player_tag, count(player_tag) as player_count from
  joined_data where ", x ," is NULL
      group by player_tag
      order by player_count DESC
      limit 100", sep = ""))
  if(dim(tble)[1] != 0){
    vars_with_NA = append(vars_with_NA, x)
  }
}
```

```{r, variables with nulls}
vars_with_NA
```

## Checking missing data

After going through and looking at handful of the variables, I have determined that if one of the variables is null, all variables printed above for the same case are null. The section below is used to check how many players have missing data and how that will affect

```{r}

sqldf("select player_tag, count(player_tag) as player_count from joined_data
      where (1=1)
      group by player_tag 
      order by player_count DESC
      limit 100")
#temp
```

```{r}
# Comparing above query to see if all player cases are null for a specific variable or if its actually a case by case player
player_null = sqldf("select player_tag, count(player_tag) as missing_count from joined_data
      where (1=1)
      and demo_taken is NULL
      group by player_tag 
      order by missing_count DESC
      limit 100")
player_null
```


# Visuals for conjecture about data

```{r}
sqldf("select player_tag, count(player_tag) as player_count from mp
group by player_tag
order by count(player_tag) desc") %>% 
  ggplot()+
  geom_histogram(aes(x = player_count),
                 alpha = 0.8, fill = "violet")+
  labs(title = "Player Frequency", x = "Player Count")+
  theme_minimal()
```

```{r, fig.width = 9, fig.height= 8}
# Has a decent run time. 
#joined_data %>% pairs()
```


###Correlation Plot
```{r}
corPlot(joined_data[,4:11], cex = .9, xlas = 2)
```


###Relationship between goals and saves

```{r}
joined_data %>% ggplot() +
  geom_jitter(aes(x = core_goals, y = core_saves),
             alpha = 0.2, color = "purple")+
  geom_smooth(aes(x = core_goals, y = core_saves),
            color = "red")+
  geom_vline(aes(xintercept = core_goals), alpha = 0.75, col = "gray")+
  labs(title = "Relationship between saves and goals",
       x = "# of Goals", y = "# of Saves",
       caption = "Each point is a player in a singular game")+
  theme_minimal()
```

```{r}

ggplot(joined_data)+
  geom_point(aes(y = advanced_rating, x = core_goals))

ggplot(joined_data)+
  geom_point(aes(y = advanced_rating, x = core_assists), col = "blue")
```





```{r}
joined_data %>% 
  ggplot()+
  geom_histogram(aes(x = demo_taken, fill = "Demos Taken"),
                 binwidth = 1,
                 alpha = 0.75)+
  geom_histogram(aes(x = demo_inflicted, fill = "Demos"),
                 binwidth = 1,
                 alpha = 0.4)+
  labs(x = "Times Demo'd", y = "Demos",
       title = "Demos against times demo'd",
       caption = "Greyish-blue is where numbers overlap")+
  theme_minimal()
 
```


```{r}
joined_data %>% ggplot()+
  geom_boxplot(aes(x = color, y = advanced_rating, fill = color))
```



# Checking to see if there is a difference in stats when stratifiying by team colors.
```{r}
o_adv = sqldf("select mp.advanced_rating,
mt.color,
mp.player_tag,
mp.core_goals,
mp.core_assists, 
mp.core_saves, 
mp.core_shots,
mp.core_score,
mp.demo_inflicted,
mp.demo_taken
from mt
left join mp on mp.team_id = mt.team_id
and mp.match_id = mt.match_id
where mp.advanced_rating is not null and
mp.demo_taken is not null and
mt.color = \"orange\"
limit 12810")

b_adv = sqldf("select mp.advanced_rating,
mt.color,
mp.player_tag,
mp.core_goals,
mp.core_assists, 
mp.core_saves, 
mp.core_shots,
mp.core_score,
mp.demo_inflicted,
mp.demo_taken
from mt
left join mp on mp.team_id = mt.team_id
and mp.match_id = mt.match_id
where mp.advanced_rating is not null and
mp.demo_taken is not null and
mt.color = \"blue\"
limit 12810")
```


```{r}
t.test(x = b_adv$advanced_rating, y = o_adv$advanced_rating)
```


```{r}
t.test(x = b_adv$core_score, y = o_adv$core_score)

```
```{r}
t.test(x = b_adv$core_goals, y = o_adv$core_goals)
```


So there is a significant difference between advanced player rating when comparing team color. In other words, it's expected that that the players on the blue team will have a higher advanced rating than players on the orange team. The same can be said for score and goals.


